\documentclass{article}
\include{header}

\begin{document}
\rating{2}{2}
Euler's well is a labeling of the $n \times k$ grid with a permutation in
$S_{n \times k}$ such that the upper left corner is labeled with $1$.
\begin{quote}
  Water is poured into the well from a point above the section marked 1, at the rate of 1 cubic foot per minute. Assume that water entering a region of constant depth immediately disperses to all orthogonally adjacent lower-depth regions evenly along that region’s exposed perimeter (an assumption that Euler insisted on).

After how many minutes will the water begin to accumulate in
[the lower right corner]?
\end{quote}

\begin{figure}[ht!]
  \centering
  \begin{tikzpicture}
    \draw[dashed, very thick] (0,0) grid (5,5);
    \foreach \i/\j/\n in {
      0/4/1, 1/4/14, 2/4/9, 3/4/20, 4/4/3,
      0/3/5, 1/3/13, 2/3/24, 3/3/17, 4/3/18,
      0/2/25, 1/2/16, 2/2/4, 3/2/21, 4/2/6,
      0/1/10, 1/1/2, 2/1/15, 3/1/19, 4/1/23,
      0/0/7, 1/0/22, 2/0/8, 3/0/12, 4/0/11,} {
      \node at (\i + 0.5, \j + 0.5) {\n};
    }
  \end{tikzpicture}
  \caption{
    A labeling of the $5 \times 5$ grid where the labels are a permutation of
    the integers from $1$ to $25$.
  }
\end{figure}
\begin{question}
  For a random permtation in $S_{n \times k}$, what is the expected amount of
  time it takes for water to reach the lower right hand corner of the grid?
\end{question}

\begin{related}
  \item What if water can flow diagonally?
  \item What if the source or sink are in different places? What if there are
  multiple sources/sinks?
  \item What if this is done on a torus? Triangular/hexagonal grid? Three
  dimensions?
  \item What if the numbers are not neccesarily a permutation?
  \item What if the well is a Latin square?
  \item What is an efficient algorithm for computing this for an arbitrary
  permutation?
  \item What is the expected value of number of ``wet'' squares at the end?
  \item How many wells have minimal filling times?
  \item How many wells up to ``fill level''? (e.g. two wells are equivalent if
  each square has the same height after the water flows all the way)
\end{related}

\begin{references}
  \item \url{http://chalkdustmagazine.com/blog/well-well-well/}
  \item \url{https://oeis.org/A321853}
\end{references}

\end{document}
